\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\begin{document}

\begin{center}
{\LARGE\textbf{Hotel Discovery Questions}}\\[0.3cm]
{\small Sales Conversation Guide}\\[1cm]
\end{center}

\hrule
\vspace{1cm}

\section*{Current Operations}

\begin{enumerate}
    \item How many phone calls does your hotel receive per day?
    \item What percentage of calls go unanswered or to voicemail?
    \item Who answers your phones - front desk or dedicated staff?
    \item What are your busiest call times?
    \item Do you offer 24/7 phone support?
\end{enumerate}

\section*{Pain Points}

\begin{enumerate}
\setcounter{enumi}{5}
    \item What frustrates you most about phone-based bookings?
    \item Have you calculated revenue lost from missed calls?
    \item Do front desk staff feel overwhelmed with calls?
    \item How do you handle calls during check-in/check-out rush?
    \item What happens when someone calls after hours?
\end{enumerate}

\section*{Guest Experience}

\begin{enumerate}
\setcounter{enumi}{10}
    \item How important is phone booking to your guests?
    \item Do you get international calls? Which languages?
    \item What questions do callers ask most often?
    \item How do guests feel about automated phone systems?
    \item Any complaints about wait times or missed calls?
\end{enumerate}

\section*{Current Technology Stack}

\begin{enumerate}
\setcounter{enumi}{15}
    \item What Property Management System (PMS) do you use? (Opera, Cloudbeds, Mews, RoomRaccoon, etc.)
    \item What is your current phone system provider? (Avaya, Cisco, RingCentral, basic landline?)
    \item Do you use a Channel Manager? Which one?
    \item What booking engine powers your website reservations?
    \item Do you have a CRM system for guest data?
    \item What payment processor do you use? (Stripe, Square, integrated with PMS?)
    \item Do you use any call recording or analytics tools currently?
    \item Is your tech managed in-house or by a vendor?
\end{enumerate}

\section*{Integration Requirements}

\begin{enumerate}
\setcounter{enumi}{23}
    \item Does your PMS have an API or allow third-party integrations?
    \item Can you forward calls to a different number, or do you need on-premise integration?
    \item Who manages your phone system - can they make routing changes?
    \item Do you have IT staff or rely on external support?
    \item What integrations are must-haves vs nice-to-haves?
\end{enumerate}

\section*{Decision Making}

\begin{enumerate}
\setcounter{enumi}{28}
    \item Who else would be involved in this decision?
    \item What would success look like for you?
    \item Do you have budget allocated for technology this year?
    \item What concerns do you have about AI answering phones?
\end{enumerate}

\section*{Feedback \& Suggestions}

\begin{enumerate}
\setcounter{enumi}{32}
    \item What features would be most valuable to you?
    \item Is there anything you wish your current phone system could do?
    \item What would make you say ``this is exactly what we need''?
    \item Any past experiences with vendors that worked well or poorly?
    \item What would you change about how phone bookings work today?
\end{enumerate}

\vfill

\begin{center}
\hrule
\vspace{0.5cm}
{\small Lumentra AI - Hotel Voice Agent}
\end{center}

\end{document}
