\documentclass[11pt,a4paper]{article}

% Basic packages only
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}

% Simple formatting
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

\begin{document}

% Title
\begin{center}
{\Huge\textbf{Lumentra AI}}\\[0.5cm]
{\Large Intelligent Voice Agent for Hotels}\\[1cm]
{\large Never Miss a Booking Again}\\
{\small 24/7 AI-Powered Phone Answering Service}\\[2cm]
{\large\textbf{Product Overview \& Discovery Guide}}\\[0.5cm]
{\small Confidential Business Document}\\
{\small \today}
\end{center}

\newpage

\tableofcontents

\newpage

\section{Executive Summary}

\textbf{Lumentra AI} is a white-label voice agent platform that answers phone calls for hotels 24/7. Our AI agent handles reservations, answers common questions, and transfers to staff only when necessary.

\subsection{The Problem We Solve}

Hotels face critical challenges with phone-based bookings:

\begin{itemize}
    \item \textbf{Missed Revenue:} 30-40\% of calls go unanswered during peak hours or after hours
    \item \textbf{Staff Overload:} Front desk staff juggle walk-ins, check-ins, and phone calls
    \item \textbf{Inconsistent Service:} Quality varies based on who answers and when
    \item \textbf{Language Barriers:} Limited multilingual support for international guests
    \item \textbf{High Labor Costs:} 24/7 phone coverage requires multiple shifts
\end{itemize}

\subsection{Our Solution}

An AI voice agent that:
\begin{itemize}
    \item Answers every call within 2 rings, 24/7/365
    \item Books reservations directly into your system
    \item Answers FAQs (check-in times, amenities, directions, policies)
    \item Transfers to staff for complex requests
    \item Speaks naturally with human-like conversation
\end{itemize}

\subsection{Key Benefits}

\begin{center}
\begin{tabular}{|l|c|c|}
\hline
\textbf{Metric} & \textbf{Before} & \textbf{After Lumentra} \\
\hline
Calls Answered & 60-70\% & \textbf{100\%} \\
Average Wait Time & 45+ seconds & \textbf{< 3 seconds} \\
After-Hours Coverage & Limited/None & \textbf{Full 24/7} \\
Cost per Call & \$3-5 (staff time) & \textbf{\$0.15-0.25} \\
Booking Conversion & Varies & \textbf{+15-25\%} \\
\hline
\end{tabular}
\end{center}

\newpage

\section{Core Features}

\subsection{Intelligent Call Handling}

\begin{itemize}
    \item \textbf{Natural Conversation:} AI speaks like a trained front desk agent, not a robot
    \item \textbf{Context Awareness:} Remembers conversation context throughout the call
    \item \textbf{Interruption Handling:} Caller can interrupt at any time (barge-in support)
    \item \textbf{Sentiment Detection:} Recognizes frustrated callers and adjusts tone
\end{itemize}

\subsection{Reservation Management}

\begin{itemize}
    \item \textbf{Real-Time Availability:} Checks your actual inventory before offering dates
    \item \textbf{Instant Booking:} Creates confirmed reservations during the call
    \item \textbf{Confirmation Codes:} Provides verbal confirmation with code
    \item \textbf{SMS Confirmation:} Sends text confirmation after booking
\end{itemize}

\subsection{Smart Escalation}

\begin{itemize}
    \item \textbf{Knows When to Transfer:} Complex requests go to your staff
    \item \textbf{Warm Handoff:} Summarizes conversation before transfer
    \item \textbf{Voicemail Fallback:} Takes detailed messages if staff unavailable
    \item \textbf{Priority Routing:} VIP callers can be fast-tracked
\end{itemize}

\subsection{Analytics Dashboard}

\begin{itemize}
    \item \textbf{Real-Time Monitoring:} See active calls and agent status
    \item \textbf{Call Analytics:} Duration, outcomes, booking conversion rates
    \item \textbf{Revenue Tracking:} Bookings attributed to AI agent
    \item \textbf{Transcripts:} Full searchable transcripts of every call
\end{itemize}

\newpage

\section{Hotel-Specific Customization}

Every hotel is unique. Lumentra adapts to your brand and operations:

\subsection{Voice \& Personality}

\begin{tabular}{|l|l|}
\hline
\textbf{Setting} & \textbf{Options} \\
\hline
Voice & Male/Female, multiple accents, custom voice cloning \\
Tone & Professional, Friendly, Luxury, Casual \\
Speaking Speed & Adjustable for clarity \\
Name & Your choice (e.g., ``Hi, this is Sarah from The Grand Hotel'') \\
\hline
\end{tabular}

\subsection{Greetings \& Responses}

\begin{itemize}
    \item \textbf{Standard Greeting:} ``Thank you for calling [Hotel Name], this is [Agent]. How may I assist you?''
    \item \textbf{After-Hours:} ``Good evening! Our front desk is currently closed, but I can help with reservations...''
    \item \textbf{Holiday Greeting:} Custom messages for special occasions
    \item \textbf{Busy Periods:} ``We're experiencing high call volume, thank you for your patience...''
\end{itemize}

\subsection{Knowledge Base}

The AI is trained on your hotel's specific information:

\begin{itemize}
    \item Room types, rates, and amenities
    \item Check-in/check-out times
    \item Parking, pet, and cancellation policies
    \item Local attractions and directions
    \item Restaurant hours and menus
    \item Spa and fitness center details
\end{itemize}

\newpage

\section{Pricing Model}

\subsection{Simple, Transparent Pricing}

\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Plan} & \textbf{Starter} & \textbf{Professional} & \textbf{Enterprise} \\
\hline
Monthly Base & \$99 & \$249 & Custom \\
Included Minutes & 500 & 2,000 & Unlimited \\
Overage Rate & \$0.20/min & \$0.15/min & Negotiated \\
SMS Confirmations & Yes & Yes & Yes \\
Live Dashboard & Yes & Yes & Yes \\
Custom Voice & No & Yes & Yes \\
API Integration & No & Yes & Yes \\
Priority Support & No & No & Yes \\
\hline
\end{tabular}
\end{center}

\subsection{ROI Example}

For a 50-room boutique hotel:

\begin{itemize}
    \item Average missed calls per month: 150
    \item Booking conversion rate: 20\%
    \item Average booking value: \$250
    \item \textbf{Recovered revenue:} 150 x 20\% x \$250 = \textbf{\$7,500/month}
    \item \textbf{Lumentra cost:} \$249/month
    \item \textbf{Net ROI: 30x return}
\end{itemize}

\newpage

\section{Upcoming Features \& Add-Ons}

\subsection{Phase 1 (Q1 2025)}

\begin{itemize}
    \item \textbf{Multilingual Support:} Spanish, French, German, Mandarin, Japanese
    \item \textbf{PMS Integration:} Direct sync with Opera, Cloudbeds, Mews, RoomRaccoon
    \item \textbf{Outbound Calls:} Booking confirmations, reminder calls
    \item \textbf{WhatsApp/SMS Bot:} Same AI, text-based channels
\end{itemize}

\subsection{Phase 2 (Q2-Q3 2025)}

\begin{itemize}
    \item \textbf{Upselling Engine:} Suggests room upgrades, packages during booking
    \item \textbf{Dynamic Pricing Awareness:} Quotes rates based on demand
    \item \textbf{Guest Recognition:} Identifies returning guests, personalizes service
    \item \textbf{Concierge Services:} Books restaurant reservations, tours, transportation
\end{itemize}

\subsection{Phase 3 (Q4 2025)}

\begin{itemize}
    \item \textbf{Voice Biometrics:} Secure verification for loyalty members
    \item \textbf{Predictive Analytics:} Forecasts call volume, suggests staffing
    \item \textbf{Multi-Property Support:} Central agent handles multiple hotels
    \item \textbf{Review Response:} AI responds to online reviews (TripAdvisor, Google)
\end{itemize}

\newpage

\section{Discovery Questions for Hotel Owners}

Use these questions during sales conversations to understand customer needs and tailor the pitch.

\subsection{Current Operations}

\begin{enumerate}
    \item How many phone calls does your hotel receive per day on average?
    \item What percentage of calls would you estimate go unanswered or to voicemail?
    \item Who currently answers phone calls? Front desk? Dedicated staff?
    \item What are your busiest call times? Do you have coverage gaps?
    \item Do you offer 24/7 phone support? If not, what are your hours?
\end{enumerate}

\subsection{Pain Points}

\begin{enumerate}
\setcounter{enumi}{5}
    \item What is your biggest frustration with phone-based bookings today?
    \item Have you ever calculated how much revenue you lose from missed calls?
    \item Do your front desk staff feel overwhelmed juggling calls and guests?
    \item How do you handle calls during check-in/check-out rush hours?
    \item What happens when someone calls after hours with an urgent request?
\end{enumerate}

\subsection{Guest Experience}

\begin{enumerate}
\setcounter{enumi}{10}
    \item How important is phone-based booking to your guest demographic?
    \item Do you receive calls from international guests? In what languages?
    \item What are the most common questions callers ask?
    \item How do guests typically feel about automated phone systems (IVR)?
    \item Have you received complaints about phone wait times or missed calls?
\end{enumerate}

\subsection{Technology \& Integration}

\begin{enumerate}
\setcounter{enumi}{15}
    \item What Property Management System (PMS) do you currently use?
    \item Do you have a central reservation system or booking engine?
    \item How tech-savvy is your staff? Would they be comfortable with a new dashboard?
    \item What other software tools does your hotel use (CRM, channel manager)?
    \item Have you tried any AI or automation tools before? What was your experience?
\end{enumerate}

\subsection{Decision Making}

\begin{enumerate}
\setcounter{enumi}{20}
    \item Who else would be involved in a decision like this?
    \item What would success look like for a solution like this?
    \item Do you have a budget allocated for technology improvements this year?
    \item What concerns would you have about an AI answering your phones?
    \item Would you be interested in a pilot program to test with limited risk?
\end{enumerate}

\newpage

\section{Common Objections \& Responses}

\subsection{``Our guests want to talk to a real person''}

\textit{Response:} We understand. That's why our AI is designed to sound natural and conversational, not robotic. It handles routine calls (availability, bookings, FAQs) so your staff can focus on guests who need personal attention. The AI always offers to transfer to a staff member for complex requests. Many hotels find that guests appreciate immediate answers over waiting on hold.

\subsection{``We already have a phone system / IVR''}

\textit{Response:} Traditional IVR systems make callers press buttons and navigate menus. Our AI has a natural conversation---no menus, no ``press 1 for reservations.'' Callers just talk, and the AI understands and responds. It's like having your best front desk agent available 24/7.

\subsection{``What if the AI makes a mistake?''}

\textit{Response:} Every call is recorded and transcribed. You can review any conversation. The AI is trained to say ``let me transfer you to a team member'' when it's unsure, rather than guessing. We also have human-in-the-loop support for edge cases.

\subsection{``We're a small hotel, we don't get that many calls''}

\textit{Response:} Even better---our Starter plan is \$99/month with 500 minutes. If you only get 5 calls a day, that's still 150+ calls per month. If just one call converts to a booking that would have been missed, the system pays for itself. And as you grow, we scale with you.

\subsection{``How long does setup take?''}

\textit{Response:} Most hotels are live within 48 hours. We configure the AI with your hotel information, set up your phone routing, and train your staff on the dashboard. No IT department needed.

\newpage

\section{Next Steps}

\subsection{For Interested Hotels}

\begin{enumerate}
    \item \textbf{Discovery Call:} 30-minute conversation to understand your needs
    \item \textbf{Demo:} Live demonstration of the AI agent with your hotel's information
    \item \textbf{Pilot Program:} 2-week free trial with limited call volume
    \item \textbf{Full Deployment:} Go live with full integration and support
\end{enumerate}

\subsection{Contact Information}

\begin{center}
\begin{tabular}{ll}
\textbf{Website:} & www.lumentra.ai \\
\textbf{Email:} & sales@lumentra.ai \\
\textbf{Phone:} & (555) 123-4567 \\
\end{tabular}
\end{center}

\vspace{2cm}

\begin{center}
\rule{10cm}{0.5pt}

\vspace{0.5cm}

\textit{``Lumentra turned our after-hours calls from missed opportunities into confirmed bookings. The ROI was immediate.''}

\vspace{0.3cm}

--- \textbf{General Manager, Boutique Hotel Group}
\end{center}

\end{document}
